COL772: Project Proposal

### 2018-03-20 proposal/proposal.tex
Added final proposal submission

\section{Dataset}
We plan to use the Marsan Ma’s curated twitter corpus of $800,000$ context-responses\cite{data:twitter-marson} for our baseline model testing. Later, we can actually use the twitter streaming API to mine tweets and their corresponding replies to create our own dataset in a day or so.\\
We can later extend the dataset by merging it with the Enron Email Dataset, which contains about $500k$ emails of $150$ employees of Enron Corporation\cite{data:enron}. \\
If, time permits, we can concatenate the Cornell Movie-Dialogs corpus \cite{data:cornell-movie} in addition to the Twitter corpus to train a better model.

>>>>

\section{Dataset}
We plan to use the Marsan Ma’s curated twitter corpus of $800,000$ context-responses\cite{data:twitter-marson} for our baseline model testing. Later, we can use the twitter streaming API to mine tweets and their corresponding replies to create our own dataset in a day or so.\\
We can later extend the dataset by merging it with the Enron Email Dataset, which contains about $500k$ emails of $150$ employees of Enron Corporation\cite{data:enron}. \\
If, time permits, we can concatenate the Cornell Movie-Dialogs corpus \cite{data:cornell-movie} in addition to the Twitter corpus to train a better model.
